Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-04-30 analysis/paper/paper.Rmd
Attempts to address faceting problem again with command; paper html may or may not work.

JOEL - this graph below looks VERY good zoomed in, but kinda crowded in HTML; still working on a better way to facet with specified rows
```{r Fig-SurveyTiming2, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap=""}

>>>>

JOEL - I specified ncol = 3 in the facet command but my html doesn't update with it (I know the command itself works since I can see the zoom in the script)? Are you able to see it? and/or does it work in solving the space problem?
```{r Fig-SurveyTiming2, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap=""}
